Sex-based analysis/Differences in TB Immune Activation

### 2025-04-24 products/manuscript/Manuscript.qmd
stage all changes to the files

---
title: "Example Manuscript Template for a Data Analysis Project"
author: "Doreen Kibuule Kalembe"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---

>>>>

---
title: "Sex-based analysis/Differences in TB Immune Activation"
author: "Doreen Kibuule Kalembe"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/american-journal-of-epidemiology.csl
---
